Primal-dual algorithm for computing Nash equilibria in sequential games with imcomplete information

### 2014-12-16 nips2015.tex
more enh wip

\begin{abstract}
We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
\end{abstract}

\section{Introduction}
\label{sec:intro}
For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential in the size of the game tree.

@@

%%%
\paragraph{Extensive-form representation}
The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically.
The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.

At each node $t$ of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

@@

\paragraph{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, $\sigma_h$ is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. \textit{Perfect recall} means that a player cannot get additional information on the game treee by remembering their earlier choices. $C_h$ is the set of choices at $h$. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players (the other player, and the \textit{chance} player, aka \textit{nature}) deleted. Such a sequence represents a possible sequence of choices made by player $k$ in the game, from start to finish.

$\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
\begin{equation}
    z(\emptyset) = 1 \text{ and }
    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

A realization plan $z$ for a player $k$ induces a \textit{behavioural-strategy} $\beta_k$ defined by
\begin{equation}
  \beta_k(c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

where $h \in \mathcal{I}_k$ and $c \in \mathcal{C}_h$, and $\beta_k(c)$ is the probability to play $c$ given that the player is at information set $h$. From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

These linear constraints \eqref{eq:lin} can be written in the form
\begin{equation}
  E_k z = e_k
\end{equation}

where $E_k$ a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$.

The \textit{strategy profile} of player $k$ is then the $n_k$-dimensional polytope

@@

Player $k$'s \textit{pure} strategies correspond to their sequences $\mathcal{S}_k$, and a realization plan is simply a randomization on these pure strategies.

$A$, an $n_1$-by-$n_2$ matrix, is the \textit{payoff matrix} from player 1's perspective of the game. Formally $A = (A_{\sigma,\tau})$, where
  \begin{equation}
    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
  \end{equation}

@@

The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form. However, since were are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all required information, as we will see in the next section.

\paragraph{Nash equilibrium problem in sequence-form representaion}
In sequence-form representation, the Nash equilibrium problem is (see \cite{von1996efficient})
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
  \label{eq:opt_pb}
\end{equation}
As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution iff
\begin{equation}
  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

@@

\section{The algorithm}
We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}. The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}. Though this scheme has recently gained considerable popularity in the signal processing community
%\cite{gramfort-etal:2013a}
, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.

@@

\section{Application to Poker: Kuhn Poker}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left[\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right]$,\\
$E_1 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
and $E_2 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right]$.\\
The pair $(x^*, y^*)$ of realization plans given by\\
$x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}. The convergence curve is shown in Fig \ref{Tab:conv_curves}. One easy checks that this equilibrium is feasible. Indeed,  $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$ and $E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T$. Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.

@@

\section{Extending to games with more general strategy profiles of a similar type}
Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
\end{equation}

@@

As a motivating example, suppose Alice knows a prior that Bob is playing given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$). Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
\begin{equation}
  x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
\end{equation}

@@

\begin{proof}
Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
$i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ replaced with $\Pi_{C_k}$.
\end{proof}

>>>>

\begin{abstract}
We present a simple $\mathcal{O}(1/\epsilon)$ primal-dual algorithm with a low cost per iteration, for computing Nash equilibria in two-person zero-sum sequential games like Texas Hold'em Poker. %% Our algorithm is applicable to a broad class of two-person zero-sum games including simultaneous games and sequential games with imcomplete information and perfect recall. The applicability to the latter kind of games is thanks to the sequence-form representation von Stengel's \cite{von1996efficient}
Our algorithm derives from the general primal-dual algorithm developed
% by Chambolle and Pock
in \cite{chambolle2010}, which has received considerable interest in the signal processing community, but is not directly applicable to the saddle-point problem corresponding to Nash equilibria since the strategy profiles (polytopes) of players are so complex that it is not possible
% (for example, simplexes for simultaneous games, and intersections of hyperplanes and nonnegative orthants, for sequential games)
 to analytically compute
% (i.e using non-iterative procedures, etc.)
euclidean
% (metric)%
 projections (the proximal operators) thereupon.
Our technique is to dualize the linear constraints that form part of the player's strategy profile, thus obtainining an equivalent saddle-point problem which is more amendable to the primal-dual scheme, without any additional overhead. The resulting algorithm is simple, only involving matrix-vector multiplications
% (without any matrix inversions, etc.)
and nonnegative clipping.
% (taking point-wise max of a vector and 0)
The $\mathcal{O}(1/\epsilon)$ convergence rate of our algorithm derives explicitly from the general primal-dual algorithm in \cite{chambolle2010}. Unlike the EGT (Excessive Gap Technique) recently used in \cite{hoda2010smoothing}, our algorithm has a cheap and constant cost per iteration. As proof of concept, we apply our algorithm to solve Kuhn Poker.
We conclude by extending our results to tackle Nash equilibrium problems with even more general strategy profiles, where the nonnegativity constraints on realization plans are replaced with general convex sets.
\end{abstract}

\section{Introduction}
\label{sec:intro}
For sequential games with imcomplete information and perfect recall like Texas Hold'em Poker, von Stengel and co-workers have developed the \textit{sequence-form} representation (see \cite{von1996efficient} and references therewithin), whose size is linear in the size of the game tree, in contrast with the \textit{strategic-form} representation which is exponential. The goal of this paper is to develop a fast and simple primal-dual algorithm for computing Nash equilibria for such games, using this representation.

\paragraph{Plan}
We first briefly introduce the sequence-form representation, and contrast it to the strategic-form representation. Then we state the Nash equilibrium problem for the sequence-form representation. In section \ref{sec:algo} we derive the proposed algorithm for solving this problem and prove its $\mathcal{O}(1/\epsilon)$ convergence rate.  This is followed by a demonstration on Kuhn Poker in section \ref{sec:kuhn}. In section \ref{sec:algo_gen}, we extend  the algorithm to problems with more general strategy profiles, and exhibit thesame convergence properties.

@@

%%%
\paragraph{Extensive-form representation}
The game consists of three players: player 1 (Alice), player 2 (Bob), and player 0, a special player called \textit{chance}. All three players are treated symmetrically.
The players take turns to play according to the rules of the game, until a terminal node (aka \textit{leaf}) is reached upon which the game automatically stops. %% The sequence-form is similar to the \textit{extensive-form} except that in the latter, pure strategies are defined on edges, whilst they're defined on paths (sequences of ordered choices) in the former.
At each node $t$ of the \textit{game tree}, a unique player \textit{acts} (ie take their turn), referred to as the \textit{player to act} at the given node. This way, the nodes of the game tree are partitioned into three classes: the nodes at which the chance player acts (e.g the root node), the nodes at which Alice acts, and the nodes at which Bob acts. Due to imcompleted information, each player's nodes are grouped into equivalent classes of \textit{strategically indistinguishable} nodes called \textit{information sets}; $\mathcal{I}_k$ is the set of all information sets of player $k$. If each information set is a singleton, then the game reduces to a game complete information.

@@

\paragraph{From extensive-form to sequence-form representation}
For each information set $h$ of player $k$, $\sigma_h$ is the sequence of choices from the root node, to --any node of-- $h$, ignoring the choices of the other players. $C_h$ is the set of choices at $h$. \textit{Perfect recall} means that a player cannot get additional information on the game tree by remembering their earlier choices. The set of \textit{sequences} of player $k$, denoted $\mathcal{S}_k$, is defined by 
\begin{equation}
\mathcal{S}_k := \{\emptyset\} \cup \{\sigma_h c\text{ } |\text{ } h \in I_k, c \in C_h\}
\end{equation}
Each element $\sigma$ of $\mathcal{S}_k$ is a path joining the root node to a leaf in the game tree, with the choices of all other players deleted, and represents a possible sequence of choices made by player $k$ in the game, from start to finish. $\sigma_k(t)$ is the unique sequence in $\mathcal{S}_k$ which can be extended to the path from root to node $t$, by including the choices of the other players;
$\beta_0(t)$ is the product of the probabilities of the choices made by the chance player along $\sigma_0(t)$.

Player $k$'s \textit{pure-strategies} correspond to points in $\prod_{h \in \mathcal{I}_k}{\mathcal{C}_h}$, and their \textit{mixed-strategies} are randomizations on these pure-strategies. In sequence-form, the strategy profile $Q_k$ of player $k \ge 1$ is the polytope of $n_k$-dimensional nonnegative vectors satisying
% Besides nonnegativity, the \textit{realization plans} $z$ of each play $k>0$ must obey linear contraints of the form
\begin{equation}
    z(\emptyset) = 1 \text{ and }
    z(\sigma_h) - \sum_{c \in C_h}{z(\sigma_h c)} = 0\text{, } \forall h \in \mathcal{I}_k
  \label{eq:lin}
\end{equation}

These linear constraints \eqref{eq:lin} can be succinctly written as $E_k z = e_k$,
where $E_k$ is a matrix with $p_k := 1 + \#\mathcal{I}_k$ rows and $n_k := \#\mathcal{S}_k$ columns whose entries are either $-1$, $0$, or $1$, and $e_k$ is $p_k$-dimensional vector of the form $(1, 0, ..., 0)$. Thus we can re-write

@@

Each point $z \in Q_k$ are called \textit{realization plan} and induces a \textit{behavioural-strategy} $\beta_k$ such that for each information set $h \in \mathcal{I}_k$ and each choice $c \in C_h$, the probability for player $k$ to make a choice $c \in \mathcal{C}_h$ from any node in $h$ is
\begin{equation}
  \beta_k(h, c) := \begin{cases}
    z(\sigma_hc)/z(\sigma_h), é\mbox{if } z(\sigma_h) > 0\\
    0, &\mbox{Otherwise}.
  \end{cases}
\end{equation}

From this definition, it is clear that each behavioural-strategy is equivalent to a mixed-strategy.

The \textit{payoff matrix} from player 1's perspective is the the $n_1$-by-$n_2$ matrix $A = (A_{\sigma,\tau})$ defined by
\begin{equation}
    A_{\sigma,\tau} := \sum_{\text{leafs }t\text{ : } \sigma_1(t) = \sigma\text{ and } \sigma_2(t) = \tau}{\beta_0(t)a(t)}, \forall (\sigma, \tau) \in \mathcal{S}_1 \times \mathcal{S}_2
  \end{equation}

@@

The nanuplet $(\mathcal{I}_1, \mathcal{I}_2, \mathcal{S}_1, \mathcal{S}_2, A, E_1, E_2, e_1, e_2)$ completely specifies a game in sequence-form. However, since are only interested in computing Nash equilibria, the quintuplet $(A, E_1, E_2, e_1, e_2)$ conveys all the needed data.

\paragraph{Statement of the problem: Nash equilibrium problem in sequence-form}
In sequence-form representation, the Nash equilibrium problem is (see \cite{von1996efficient})
\begin{equation}
  \underset{y \in Q_2}{minimize}\text{ }\underset{x \in Q_1}{maximize}\text{ }{x^TAy}
  \label{eq:opt_pb}
\end{equation}
As usual, the ``minimax'' notation in problem \eqref{eq:opt_pb} means that a pair $(x^*, y^*) \in Q_1 \times Q_2$ is a solution if (and only if)
\begin{equation}
  x^TAy^* \le x^TAy \le {x^*}^TAy, \forall (x, y) \in Q_1 \times Q_2
\end{equation}
Such pairs $(x^*, y^*)$ correspond to the Nash equilibria of the game, and ${x^*}^TAy^*$ is the \textit{value}
\footnote{This value is the same for every equilibrium pair $(x^*, y^*)$.} of the game.

@@

\section{The algorithm}
\label{sec:algo}
We now derive our primal-dual algorithm for solving the Nash equilibrium problem \eqref{eq:opt_pb}. The algorithm is derived from the general primal-dual Algorithm 39 proposed in \cite{chambolle2010}. Though this scheme has recently gained considerable popularity in the signal processing community
%\cite{gramfort-etal:2013a}
, to the best of our knowledge, this is the first time it is being applied to compute Nash equilibria.

@@

\section{Application to Poker: Kuhn Poker}
\label{sec:kuhn}
The Kuhn 3-card Poker has sequence-form specification given by (not showing zero entries)\\
$A = \left[\begin{array}{ccccccccccccc}
  &   &   &   &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6 &  \\
  &   &   &   &   &   &   &   & -1 / 6 &   &   &   & -1 / 6\\
  &   &   &   &   &   &   &   & -1 / 3 &   &   &   & -1 / 3\\
  &   &   &   &   & 1 / 6 & -1 / 3 &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   &   &   &   &   & -1 / 6 &  \\
  &   &   &   & -1 / 6 &   &   &   &   &   &   &   & -1 / 6\\
  &   &   &   & 1 / 3 &   &   &   &   &   &   &   & -1 / 3\\
  & 1 / 6 & 1 / 3 &   &   &   &   &   &   & 1 / 6 & -1 / 3 &   &  \\
  &   &   & 1 / 6 &   &   &   & 1 / 6 &   &   &   &   &  \\
  &   &   &   & -1 / 6 &   &   &   & -1 / 6 &   &   &   &  \\
  &   &   &   & 1 / 3 &   &   &   & 1 / 3 &   &   &   &  \\
  & 1 / 6 & 1 / 3 &   &   & 1 / 6 & 1 / 3 &   &   &   &   &   &  
\end{array}\right]$,\\
$E_1 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 &   &   & 1\\
-1 & 1 &   &   & 1 &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   & 1 &   &   & 1 &   &   &   &  \\
  & -1 & 1 & 1 &   &   &   &   &   &   &   &   &  \\
  &   &   &   &   & -1 & 1 & 1 &   &   &   &   &  \\
  &   &   &   &   &   &   &   &   & -1 & 1 & 1 &  
\end{array}\right]$, $e_1 = e_2 = [1, 0, 0, 0, 0, 0, 0]^T$,\\
and $E_2 = \left[\begin{array}{ccccccccccccc}
1 &   &   &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   & 1 & 1 &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   & 1 & 1 &   &  \\
-1 &   &   &   &   & 1 & 1 &   &   &   &   &   &  \\
-1 &   &   &   &   &   &   &   &   &   &   & 1 & 1\\
-1 & 1 & 1 &   &   &   &   &   &   &   &   &   &  \\
-1 &   &   & 1 & 1 &   &   &   &   &   &   &   &  
\end{array}\right]$.\\
The pair $(x^*, y^*)$ of realization plans given by\\
$x^* = [1, 0.759, 0.759, 0, 0.241, 1, 0.425, 0.575, 0, 0.275, 0, 0.275, 0.725]^T$ and
$y^* = [1, 1, 0, 0.667, 0.333, 0.667, 0.333, 1, 0, 0, 1, 0, 1]^T$ is a Nash equlibrium for the game, computed using Algorithm  \ref{Tab:algo_simplified}. The convergence curve is shown in Fig \ref{Tab:conv_curves}. One easy checks that this equilibrium is feasible. Indeed,  $E_1x^* - e_1 = [4.76 \times 10^{-5}, -1.91 \times 10^{-5}, 5.67 \times 10^{-5}, 8.23 \times 10^{-6}, 2.90 \times 10^{-5}, -8.62 \times 10^{-7}, -1.96 \times 10^{-5}]^T$ and $E_2y^* - e_2 = [-7.04 \times 10^{-7}, 2.27 \times 10^{-6}, -3.29 \times 10^{-6}, -1.50 \times 10^{-6}, 2.92 \times 10^{-6}, -4.97 \times 10^{-7}, -5.85 \times 10^{-7}]^T$. Finally, $x^*TAy^* = -0.055593685705289997$, which agrees to 4 d.p with the value of $-1 / 18$ computed analytically by Kuhn in his 1954 paper.

@@

\section{Extending to games with more general strategy profiles}
\label{sec:algo_gen}
Notice tha in \eqref{eq:poly}, the strategy profile of player $k$ can be factored as
\begin{equation}
  Q_k := \{z \in \mathbb{R}^{n_k}_+| E_kz = e_k\text\}
\end{equation}

@@

As a motivating example, suppose Alice knows a priori that Bob is playing a given realization plan $y_0 \in Q_2$ (for example, take $y_0 = [1, 0, ..., 0]^T \in \mathbb{R}^{n_2}$). Alice seeks a \textit{best response strategy}, namely a strategy $x^* \in Q_1$ such that
\begin{equation}
  x^TAy_0 \le {x^*}^TAy_0,\text{ } \forall x \in Q_1
\end{equation}

@@

\begin{proof}
Totally analogous to the proof of Theorem \ref{thm:pd} with $\mathbb{R}^{n_k}_+$ replaced with $C_k$,
$i_{\mathbb{R}^{n_k}_+}$ replaced with $i_{C_k}$, and $\Pi_{\mathbb{R}^{n_k}_+}$ (nonnegative clipping) replaced with $\Pi_{C_k}$.
\end{proof}
